---
title: "R Notebook"
output:
  word_document: default
  pdf_document: default
  html_notebook: default
---

```{r, include=FALSE}
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyr)
```

## Read and analyse CS 11.1 SAE

```{r, include=F, echo = F}
info_raw <- read.csv("C:\\GitHubRepos\\2016_SAE_Tillage_ClimateChange\\simFiles\\SummaryResults\\all_Data.csv")

summary(info_raw)
```

# Check parameter values used in these runs

- Estimates Plant Available Soil Water (PAWC) 
- Assumes PAWC 20 cm top soil where parameters are changed

```{r, echo=FALSE}
pV <- read.csv("C:\\GitHubRepos\\2016_SAE_Tillage_ClimateChange\\ParamValues.csv")
ks <- read.csv("C:\\GitHubRepos\\2016_SAE_Tillage_ClimateChange\\KsValues.csv")
rainP <- read.csv("C:\\GitHubRepos\\2016_SAE_Tillage_ClimateChange\\RainPValues.csv")

pV$PAWC <- (pV$dul - 0.154)*200 # Assumed lower limit top soil layer and 200 mm of top soil (where param changes are made)

# tide up FIXME: do it at writing
pV$X <- NULL
ks$X <- NULL
ks$ks_value <- as.factor(as.character(round(ks$ks_value, digits=0)))
rainP$X <- NULL

```

## These are the  parameter sets

```{r}
head(pV,10)
```



## These are Ks values

```{r}
head(ks,10)
```

# Plant available soil water of each Param set

This is what results from the most current combination of parameters in the 10 parameter sets from BD ranging from 0.8 to 1.6 g/cm3

```{r, fig.width=6, fig.height=5, echo=FALSE, echo=FALSE}
pV %>%
  ggplot(aes(x=bd,y=PAWC)) +
  geom_point()+
  geom_line()+
  ylab("Plant Available Water Content in top 20 cm (mm)") +
  xlab("Bulk density (cm3/cm3)")
```

## Clean and check data

```{r, echo=FALSE}

temp1 <- info_raw %>%
  dplyr::select(-X) %>%
  filter(biomass>0) %>% # remove bad sims - FIXME: Swim not running with some params
  filter(rainSum>0) %>% # remove bad sims
  mutate(Date = dmy(Date)) %>%
  mutate(year=year(Date)) %>%
  tidyr::gather(Parameter, ParamSet, thisBD:thisSAT) %>%
  mutate(Parameter = as.factor(Parameter))

# get BD values
bdV <- pV %>% dplyr::select(code,bd) %>% mutate(ParamSet=code, bd=round(bd,1)) %>% dplyr::select(-code)

  
temp2 <- merge(temp1, ks, by="thisKS")
temp3 <- merge(temp2, bdV, by="ParamSet")
info_work <- merge(temp3, rainP, by="thisRain")

summary(info_work)


```

## Plot soil water

- Soil moisture is mainly sensitive to parameter sets (BD/DUL/SAT) when ks is 1 mm/day
- Low BD (Param set 1) has higher soil moisture than 
- interannual variability is big
- Ks >1 mm/day till 100 mm/day had almost no effect (10 panels going down)
- 

### Time series soil water


```{r, fig.width=12, fig.height=6, echo=FALSE}
info_work %>%
  filter(thisRain == 1) %>%
 # filter(thisModel=="soilWat") %>%
  filter(ks_value %in% c(1,9,62)) %>%
  mutate(ks_value=factor(ks_value, levels=c(1,9,62))) %>%
  group_by(year,thisModel,Parameter,ParamSet,thisKS,ks_value,rainP_value,bd) %>%
  filter(Parameter=="thisBD") %>%
  summarise(effect=mean(esw)) %>%
  mutate(BulkDensity=factor(bd))%>%
  ggplot(aes(x=year, y=effect, colour=BulkDensity)) +
  geom_line() + 
  geom_point(alpha=0.5) +
 # facet_grid(ks_value~thisModel+rainP_value)+
  facet_grid(ks_value~thisModel) +
  ylab("Soil water in profile (mm)") +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(text = element_text(size=20))
        
```

```{r, fig.width=12, fig.height=6, echo=FALSE}
info_work %>%
  filter(thisRain == 1) %>%
 # filter(thisModel=="soilWat") %>%
  filter(ks_value %in% c(1,9,62)) %>%
  mutate(ks_value=factor(ks_value, levels=c(1,9,62))) %>%
  group_by(year,thisModel,Parameter,ParamSet,thisKS,ks_value,rainP_value,bd) %>%
  filter(Parameter=="thisBD") %>%
  summarise(effect=mean(biomass)) %>%
  mutate(BulkDensity=factor(bd))%>%
  ggplot(aes(x=year, y=effect, colour=BulkDensity)) +
  geom_line() + 
  geom_point(alpha=0.5) +
 # facet_grid(ks_value~thisModel+rainP_value)+
  facet_grid(ks_value~thisModel) +
  ylab("Total biomass (kg/ha)") +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(text = element_text(size=20))
        
```


```{r, fig.width=12, fig.height=10, echo=FALSE}

info_work %>%
  #filter(thisRain == 1) %>%
 # filter(thisModel=="soilWat") %>%
#  mutate(thisKS = as.factor(paste0("Ks_0",thisKS))) %>%
 # mutate(ParamSet = as.factor(paste0("ParamSet_",ParamSet))) %>%
  group_by(year,thisModel,Parameter,ParamSet,thisKS,ks_value,rainP_value, bd) %>%
  filter(Parameter=="thisBD") %>%
  summarise(effect=mean(esw)) %>%
  ggplot(aes(x=factor(rainP_value), y=effect)) +
 # geom_line() + 
 # geom_point(alpha=0.5) +
  geom_jitter(position = position_dodge(width = 0.5), alpha=0.5, aes(colour=factor(bd))) +
  geom_boxplot(alpha=0.5,width = 0.5) +
  facet_grid(ks_value~thisModel) +
  ylab(" Available soil water (mm3/mm3)")
  
```

## Plot biomass

- Now Parameter sets in soil water affect yield mostly at Ks = 1 mm/day
- Interestingly, effect occurred more in "high yield" years
- Note that SWIM "breaks" and does not run at high BD parameter combinations (ask Rogerio)

```{r, fig.width=12, fig.height=10, echo=FALSE }


info_work %>%
  #filter(thisRain == 1) %>%
 # filter(thisModel=="soilWat") %>%
#  mutate(thisKS = as.factor(paste0("Ks_0",thisKS))) %>%
 # mutate(ParamSet = as.factor(paste0("ParamSet_",ParamSet))) %>%
  group_by(year,thisModel,Parameter,ParamSet,thisKS,ks_value,rainP_value, bd) %>%
  filter(Parameter=="thisBD") %>%
  summarise(effect=mean(biomass)) %>%
  ggplot(aes(x=factor(rainP_value), y=effect)) +
 # geom_line() + 
 # geom_point(alpha=0.5) +
  geom_jitter(position = position_dodge(width = 0.5), alpha=0.5, aes(colour=factor(bd))) +
  geom_boxplot(alpha=0.5,width = 0.5) +
  facet_grid(ks_value~thisModel) +
  ylab(" Available soil water (mm3/mm3)")


```

## Biomass time-series

```{r, fig.width=12, fig.height=10, echo=FALSE}
info_work %>%
#  filter(thisRain == 5) %>%
 # filter(thisModel=="soilWat") %>%
  group_by(year,thisModel,Parameter,ParamSet,thisKS,ks_value,rainP_value, bd) %>%
  filter(Parameter=="thisBD") %>%
  summarise(effect=mean(biomass)) %>%
  ggplot(aes(x=year, y=effect, colour=factor(bd))) +
 # geom_line() + 
  geom_point(alpha=0.5) +
  facet_grid(ks_value~thisModel+rainP_value)
```



## Compare the two soil water models

```{r, fig.height=10, fig.width=10}
info_work %>%
  filter(thisRain == 5) %>%
 # filter(thisModel=="soilWat") %>%
  group_by(year,thisModel,Parameter,ParamSet,thisKS) %>%
  filter(Parameter=="thisBD") %>%
  summarise(effect=mean(biomass)) %>%
  tidyr::spread(thisModel, effect) %>%
  ggplot(aes(x=soilWat, y=Swim, colour=factor(ParamSet))) +
  geom_point() +
  geom_smooth(method='lm', fill='grey') +
  facet_wrap(~thisKS, ncol=5) +
  geom_abline(intercept = 0, slope = 1)
```

## Compare rainfall scenarios


```{r, fig.height=10, include=FALSE}
info_work %>%
  filter(thisRain >= 1) %>%
 # filter(thisModel=="soilWat") %>%
  group_by(year,thisRain, thisModel,Parameter,ParamSet,thisKS) %>%
  filter(Parameter=="thisBD") %>%
  summarise(effect=mean(biomass)) %>%
  ggplot(aes(x=thisKS, y=effect, colour=factor(ParamSet))) +
  geom_point() +
  geom_smooth(method='lm', fill='grey') +
  facet_grid(ParamSet~thisRain) +
  geom_abline(intercept = 0, slope = 1)
```


## What's happened in 1988?

- Check 1988 as there were differences this year
- Note that SWIM stops at BD < 1.4

```{r, fig.width=12, fig.height=10, echo=FALSE, warning=FALSE, include = FALSE}

 info_work %>%
  filter(Parameter=="thisBD") %>%
  merge(pV, by.y="code", by.x="ParamSet") %>%
#  filter(thisKS=="3") %>%
  filter(year=="1988") %>%
  dplyr::select(year,thisModel,Parameter,ParamSet,thisKS, bd.x,biomass, drainSum, runoffSum, esSum) %>%
  tidyr::gather("OutVar","OutValue", biomass:esSum) %>%
  ggplot(aes(x=bd.x, y=OutValue, colour=thisModel)) +
  geom_point(size=2) +
  geom_line(aes(linetype=as.factor(thisKS))) +
  facet_wrap(~OutVar, scales= "free") +
 # geom_smooth(aes(fill=thisModel)) +
  xlab("Bulk density (g/cm3)")

```

## Why inter-annual variability in yield?

- Check if rainfall is the main driver of biomass differences
- Yep, it's a good part of the story it seems
- We can further analyse later (e.g. radiation, temp, etc)

```{r, echo=FALSE, fig.width=12}
  info_work %>%
#  filter(thisRain == 5) %>%
  filter(Parameter=="thisBD") %>%
  filter(ParamSet=="1") %>%
#  filter(thisKS=="1") %>%
  ggplot(aes(x=rainSum, y=biomass,colour=factor(ks_value))) +
  geom_point() +
  geom_smooth(method='lm', alpha=0.2) +
  xlab(" Accumulated rainfall during crop growth (mm)") +
  facet_grid(.~rainP_value)
```

