---
title: "R Notebook"
output: html_notebook
---

# Analysis of tillage effects undet climate change scenarios

Edmar Teixeira, Wei Hu, Adrian Hunt, Paul Johstone and John de Ruiter

# SAE 11.1 

```{r}
library(dplyr)
library(ggplot2)
library(lubridate)
library(XML)
```

# 1) Define ranges of "tillage" related parameters

Wei Hu has suggested the following parameterisation for top layer:

Conventional till:
Bulk density: <bd>1.1</bd>
Soil saturation: <sat>0.585</sat>
Soil drained upper limit: <dul>0.32</dul>
Hydraulic conductivity: <ks>2000</ks>

No-till:
Bulk density: <bd>1.4</bd>;
Soil saturation: <sat>0.472</sat>;
Soil drained upper limit: <dul>0.37</dul>;
Hydraulic conductivity: <ks>500</ks>

# 2) Sensitivity analysis 

- Take min and max of proposed ranged
- Split in 10 equally spaced values
- Run the model for each parameter

Note that they are dependent 

Set ranges of parameters (Wei Hu)
```{r}
bd_r <- c(1.1,1.4)
sat_r <- c(0.472,0.585)
dul_r <- c(0.32,0.37)
ks_r <- c(500,2000)

# creates 10 equally speced parameters within range for top soil
bd_p <- seq(from=bd_r[1], to=bd_r[2], length.out = 10)
#sat_r <- seq(from=sat_r[1], to=sat_r[2], length.out = 10)
sat_r <- 1-(bd_p/2.6) # SAT calculated from BD - need to be paired with BD values
dul_r <- seq(from=dul_r[1], to=dul_r[2], length.out = 10) # FIXME: how to get DUL from BD and align with SAT?
ks_r <- seq(from=ks_r[1], to=ks_r[2], length.out = 10) # full range to be tested in factorial
```

# Read baseline.sim files (bases for changing parameters) 

```{r}

swimSim <- "C:\\GitHubRepos\\2016_SAE_Tillage_ClimateChange\\simFiles\\Maize_SWIM3.sim"
soilWatSim <- "C:\\GitHubRepos\\2016_SAE_Tillage_ClimateChange\\simFiles\\Maize_Soilwat.sim"
  
```

# create multiple .sim files with altered parameter values

```{r}
w_model <- c("Swim","soilWat")

# Define deepest layer to respond to tillage for each model
    # Note: swim multiplies the original "Water node" layer structure in sub-layers
    # i.e. same depth of layer corresponds to a different layer number

# loop water model
  for(m in 1:length(w_model)) {

    # loop parameters' levels
    for(p in 1:length(sat_r)) {
    
    
  # read fresh base sim
  baseSim_xml_swim <- xmlTreeParse(swimSim, useInternalNodes = TRUE)
  baseSim_xml_soilWat <- xmlTreeParse(soilWatSim, useInternalNodes = TRUE) 
    
  
  # define model
  if(m==1) {
    baseSim <- baseSim_xml_swim
    tillLayer <- 5

  } else {
    baseSim <-baseSim_xml_soilWat
    tillLayer <- 2
  }
  
  # find and isolate parameter nodes
          nodesMet <- getNodeSet(baseSim, "//filename") 
          nodesOut <- getNodeSet(baseSim, "//outputfile")
          nodesBD <- getNodeSet(baseSim, "//bd")
          nodesSAT <- getNodeSet(baseSim, "//sat")
          nodesDUL <- getNodeSet(baseSim, "//dul")
          nodesKS <- getNodeSet(baseSim, "//ks")
          
          # get parameter values and 
          v1 <- sapply(nodesSAT, xmlValue)
          v2 <- as.numeric(unlist(strsplit(v1 ,split=" ")))
          v2[1:tillLayer] <- 0
         # v4 <- paste0(as.character((v3)))
          
          x <- paste(v2, sep="", collapse=" ")
          str(x)
          
 # change values
   lapply(nodesSAT, function(n) {
     xmlValue(n) = x
   })
   
          print(w_model[m])
          print(nodesSAT)
          
  } # end loop water models
  
  
} # end loop in parameter levels for sensitivity



# <bd>1.311 1.311 1.311 1.311 1.311 1.439 1.524 1.631 1.633 1.601 1.601 1.601 </bd>
# <sat>0.456 0.456 0.456 0.456 0.456 0.419 0.394 0.364 0.365 0.376 0.376 0.376 </sat>
# <dul>0.374 0.374 0.374 0.374 0.374 0.349 0.332 0.337 0.333 0.325 0.325 0.325 </dul>
# <ks>4832.039 4832.039 4832.039 4832.039 4832.039 2166.353 389.229 72.292 44.934 97.995 97.995 97.995 </ks>


```




