---
title: "R Notebook"
output: html_notebook
---

# Analysis of tillage effects undet climate change scenarios

Edmar Teixeira, Wei Hu, Adrian Hunt, Paul Johstone and John de Ruiter

# SAE 11.1 

```{r, include=FALSE}
library(dplyr)
library(ggplot2)
library(lubridate)
library(XML)
```

# 1) Define ranges of "tillage" related parameters

Wei Hu has suggested the parameterisation for top layer, I made it a bit wider.

- Take min and max of proposed ranged
- Split in 10 equally spaced values
- Run the model for each parameter

Note that they are dependent 

Set ranges of parameters (Wei Hu)
```{r}
bd_r <- c(0.8,1.6) # bulk density (g/cm3)
#sat_r <- c(0.472,0.585) # saturation (cm3/cm3) # Now calculated
# dul_r <- c(0.32,0.37) # drained upper limit (cm3/cm3) # Now calculated
ks_r <- c(1,70) # hydraulic conductivity (mm/day) # Narrow range

# creates 10 equally spaced parameters within range for top soil
bd_p <- seq(from=bd_r[1], to=bd_r[2], length.out = 10)
sat_p <- 1-(bd_p/2.65) # SAT calculated from BD - need to be paired with BD values
dul_p <- sat_p * seq(from=0.5, to=0.8, length.out = 10) # bit beyond Wei's tange of 0.6 to 0.7
#dul_p <- seq(from=dul_r[1], to=dul_r[2], length.out = 10) # FIXME: how to get DUL from BD and align with SAT?
ks_p <- seq(from=ks_r[1], to=ks_r[2], length.out = 10) # full range to be tested in factorial

parValues <- data.frame(code=c(1:10),bd=bd_p,dul=dul_p,sat=sat_p, m=dul_p/sat_p)

parValues

# save for reporting
write.csv(parValues,"C:\\GitHubRepos\\2016_SAE_Tillage_ClimateChange\\ParamValues.csv")
write.csv(data.frame(ks=c(1:10),ks_value=ks_p),"C:\\GitHubRepos\\2016_SAE_Tillage_ClimateChange\\KsValues.csv")

```

2) Set range of Ks values

- this will be used as factorial for all 10 param combinations above

```{r}
print(ks_p)
```

# 4) Read baseline.sim files 

- bases for changing parameters

```{r, include=FALSE}
baseSimFolder <- "C:\\GitHubRepos\\2016_SAE_Tillage_ClimateChange\\baseSim\\"
simFolder <- "C:\\GitHubRepos\\2016_SAE_Tillage_ClimateChange\\simFiles\\"

swimSim <- paste0(baseSimFolder, "SWIM3_base.sim")
soilWatSim <- paste0(baseSimFolder, "SoilWat_base.sim")


  
```

# 5) create multiple .sim files 

- with altered parameter values

```{r, include=FALSE}

         # function to work vector format of XML node
          
          xmlFunc <- function(vecNode, vecPar, idx, tl) {
          v1 <- sapply(vecNode, xmlValue)
          v2 <- as.numeric(unlist(strsplit(v1, split=" ")))
          v2[1:tl] <- round(vecPar[idx],3)
          v3 <- paste(v2, sep="", collapse=" ")
          return(v3)
          }


w_model <- c("Swim","soilWat")

# Define deepest layer to respond to tillage for each model
    # Note: swim multiplies the original "Water node" layer structure in sub-layers
    # i.e. same depth of layer corresponds to a different layer number

# loop water model
  for(m in 1:length(w_model)) {
    
    mod <- w_model[m]

    # loop parameters' levels
    for(p in 1:length(sat_p)) {
      
      for(k in 1:length(ks_p)) { # special case of ks that can have any value
        
  # define model
  if(m==1) {
    simXML <- xmlTreeParse(swimSim, useInternalNodes = TRUE)
    tillLayer <- 5

  } else {
    simXML <- xmlTreeParse(soilWatSim, useInternalNodes = TRUE) 
    tillLayer <- 2
  }
  
  # find and isolate parameter nodes
          nodesOut <- getNodeSet(simXML, "//outputfile")
          nodesBD <- getNodeSet(simXML, "//bd")
          nodesSAT <- getNodeSet(simXML, "//sat")
          nodesDUL <- getNodeSet(simXML, "//dul")
          nodesKS <- getNodeSet(simXML, "//ks")
          
          
          # get parameter values and 
          # v1 <- sapply(nodesSAT, xmlValue)
          # v2 <- as.numeric(unlist(strsplit(v1 ,split=" ")))
          # v2[1:tillLayer] <- round(sat_r[p],3)
          # 
          # x <- paste(v2, sep="", collapse=" ")
          # str(x)
          
 # change parameter values in XML
   lapply(nodesBD, function(n) {
     xmlValue(n) = xmlFunc(nodesBD, bd_p, p, tillLayer)
   })
   
    lapply(nodesSAT, function(n) {
     xmlValue(n) = xmlFunc(nodesSAT, sat_p, p, tillLayer)
   })
    
   lapply(nodesDUL, function(n) {
     xmlValue(n) = xmlFunc(nodesDUL, dul_p, p, tillLayer)
   })
   
   lapply(nodesKS, function(n) {
     xmlValue(n) = xmlFunc(nodesKS, ks_p, k, tillLayer)
   })
   
          print(w_model[m])
          print(nodesSAT)
          

  simName <- paste0("BD_",p,
                    "_DUL_",p,
                    "_SAT_",p,"_KS_",
                    k) # note ks
  
  
  outName <- paste0(mod,"_",simName,".out") 
  
  # change outfile name
            lapply(nodesOut, function(n) {
              xmlValue(n) = outName
            })
          
 # change attribute name of simulation 
            simNameRoot <- xmlRoot(simXML)
            xmlAttrs(simNameRoot) = c(name = paste0(mod,"_",simName))          
            
  # save XML
  saveXML(simXML, file = paste0(simFolder,"\\",mod,"_",simName,".sim"), indent=TRUE)        
          
      } # end loop in ks parameters (factorial against all other parameters)
          
  } # end loop in parameter 10 levels for sensitivity BD/DUL/SAT 
  
} # end loop water models 



# <bd>1.311 1.311 1.311 1.311 1.311 1.439 1.524 1.631 1.633 1.601 1.601 1.601 </bd>
# <sat>0.456 0.456 0.456 0.456 0.456 0.419 0.394 0.364 0.365 0.376 0.376 0.376 </sat>
# <dul>0.374 0.374 0.374 0.374 0.374 0.349 0.332 0.337 0.333 0.325 0.325 0.325 </dul>
# <ks>4832.039 4832.039 4832.039 4832.039 4832.039 2166.353 389.229 72.292 44.934 97.995 97.995 97.995 </ks>


```




